Model 

### 2019-10-01 04_estimation.Rmd
Cleanup estimation

```{r screen_pa_models}

view_kable(
htmlreg(pa_models, digits = 4, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

@@

```{r screen_obesity_models}
view_kable(
  htmlreg(obesity_models, digits = 3, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

>>>>

```{r screen_pa_models, results = "asis"}
view_kable(
htmlreg(pa_models, digits = 4, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

@@

```{r screen_obesity_models, results="asis"}
view_kable(
  htmlreg(obesity_models, digits = 3, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```
